---
title: "wholesalecustomers"
author: "Tahani AlHarbi"
date: "11/19/2020"
output: html_document
---
#### **Description:**

here I would analyze data about wholesales customers and answer some questions 
about annual spending of products in Horecia channel   

#### **data:** 
The dataset  refers to clients of a wholesale distributor.
It includes the annual spending in monetary units (m.u.) 
on diverse product categories
channel 1 Horeca channel 2 Retail  
regions: Lisbon, Porto and  other region 

Attribute Information:

- **FRESH:** annual spending (m.u.) on fresh products (Continuous);

- **MILK:** annual spending (m.u.) on milk products (Continuous);

- **GROCERY:** annual spending (m.u.)on grocery products (Continuous);

- **FROZEN:** annual spending (m.u.)on frozen products (Continuous)

- **DETERGENTS_PAPER:** annual spending (m.u.) on detergents and products (Continuous)

- **DELICATESSEN:** annual spending (m.u.)on and delicatessen products (Continuous);

- **CHANNEL:** customers Channel - Horeca (Hotel/Restaurant/Cafe) or Retail channel (Nominal)

- **REGION:** customers Region Lisnon, Oporto or Other (Nominal)




```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### **Packages**: 
load tidyverse package 
```{r}
#load packages
library(tidyverse)
```



```{r include=FALSE}
#acess data 
wholesale_customers <- read.csv("data/wholesalecustomers.csv")
```

```{r include=FALSE}

#change channel and region into factors 
wholesale_customers$Region <-  as.factor(wholesale_customers$Region) 
wholesale_customers$Channel <-  as.factor (wholesale_customers$Channel)
nlevels(wholesale_customers$Region)
nlevels(wholesale_customers$Channel)

```

```{r include=FALSE}

#rename Region 1, 2 and 3 to 
#Lisbon Porto  and Other_Region

levels(wholesale_customers$Region) <- c("Lisbon", "Porto", "Other_Region")

#rename Channel 1 to Horeca  and 2 to Retail

levels(wholesale_customers$Channel) <- c ("Horeca", "Retail")


```




```{r include=FALSE}

#make Horeca dataset and Retail dataset 

customer_horeca <- wholesale_customers%>% filter(Channel=="Horeca")
customer_retail <- wholesale_customers %>% filter (Channel=="Retail")

```

### **Exploring Data:**
 
explore the wholesalecustomers data to get know data well 

#### **Data head:**
```{r}
#Data head
knitr:: kable(head(wholesale_customers))
```


#### **Data tail:**
```{r}
#Data tail
knitr::kable(tail(wholesale_customers))
```

#### **see the proportion of 2 channels  Horica and Retail in the Data:** 
 see the prportion of channels horica and Retail  
```{r}
#see the proportion of 2 channels  Horica and Retail in the Data
ggplot(wholesale_customers, aes(Channel)) +
  geom_bar(fill = "#DD8888") 

```

#### **see the proportion of the Regions:**  
also I want to see the proportion of regions 
```{r}
#see the proportion of the Regions
ggplot(wholesale_customers,aes(Region))+ geom_bar(fill="#DD8888")
```

#### **See the max and min annual spending in the datat:**
max and min spending 
```{r}
#See the max and min annual spending in the datat
wholesale_customers %>% summarise_if(is.numeric, max)
wholesale_customers %>% summarise_if(is.numeric, min)

```

#### **See the range of Milk annual spending:** 

```{r}
#See the range of Milk annual spending
rangespendmilk <- wholesale_customers %>%
  summarise(range(Milk))

rangespendmilk

```

#### **See the range of Fresh annual spending:** 

```{r}
#See the range of Fresh annual spending
rangespendfresh <- wholesale_customers %>%
  summarise(range(Fresh))

rangespendfresh
```



#### **See the max and min spennd in Horeca Channel:** 

```{r}

#See the max and min spennd in Horeca Channel

customer_horeca %>% summarise_if(is.numeric, max)
customer_horeca %>% summarise_if(is.numeric, min)

```

#### **See the max and min spend in Chanel Retail:**

```{r}
#See the max and min spend on Chanel Retail
customer_retail %>% summarise_if (is.numeric, max)
customer_retail %>% summarise_if(is.numeric, min)


```

#### **see the annual spending on Milk:**
 
 see the annual spending on Milk product in 2 channels and 3 regions 

```{r}
#see the annual spending of Milk
ggplot(aes(x = Milk), data = wholesale_customers) +
  geom_histogram(binwidth = 1000,col="#AFC0CB") +
  xlab('Annual Spending (m.u.)') +
  ylab('Count')
```


#### **see the annual spending on Milk in Horeca channel:**

see the annual spending on Milk product in horica channel 
```{r}
#see the annual spending on Milk in Horeca channel
ggplot(aes(x = Milk), data = customer_horeca) +
  geom_histogram(binwidth = 1000,col="#AFC0CB") +
  xlab('Annual Spending (m.u.)') +
  ylab('Count')
```


#### **show the annual spending on products through channel Horeca:**

```{r}
#show the annual spending on products through channel Horeca
#Milk
ggplot( aes(x=Milk), data=customer_horeca)+geom_histogram(binwidth = 10000, col="#AFC0CB")

```

```{r}
#show the annual spending on products through channel Horeca
#Fresh
ggplot( aes(x=Fresh), data=customer_horeca)+geom_histogram(binwidth = 10000, col="#AFC0CB")
```


```{r}
#show the annual spending on products through channel Horeca
#Grosery
ggplot( aes(x=Grocery), data=customer_horeca)+geom_histogram(binwidth = 10000, col="#AFC0CB")
```


```{r}
#show the annual spending on products through channel Horeca
#Frozen
ggplot( aes(x=Frozen), data=customer_horeca)+geom_histogram(binwidth = 10000, col="#AFC0CB")
```


```{r}
#show the annual spending on products through channel Horeca
#Detergents_Paper
ggplot( aes(x=Detergents_Paper), data=customer_horeca)+geom_histogram(binwidth = 10000, col="#AFC0CB")
```

```{r}
#show the annual spending on products through channel Horeca
#Delicassen
ggplot( aes(x=Delicassen), data=customer_horeca)+geom_histogram(binwidth = 10000, col="#AFC0CB")

```


